The Mysterious Lives Of Speckles. I. Residual atmospheric speckle lifetimes in ground-based coronagraphs

### 2021-05-24 response.txt

This paper presents a semi-analytic method for calculating speckle lifetimes in idealized
coronagraphic adaptive optics systems by way of calculating the intensity PSD in the
coronagraphic focal plane. The predictions of this semi-analytic method are favorably compared
with the results of an end-to-end simulation, demonstrating the validity of the less
computationally intensive semi-analytic approach. The semi-analytic approach is used to
analyze the dependence of the speckle lifetime on parameters such as the windspeed, crossing
time, and seeing for telescopes of different aperture sizes, where complex relationships are
identified (counter to previous work). This analysis of speckle lifetimes is motivated by the
argument that the statistical lifetimes of atmospheric speckles limit the ultimate sensitivity of
ground-based high contrast imaging systems.

Overall, this paper presents useful tools that will undoubtedly be used for the planning of GSMT
extreme-AO systems. However, one of the central arguments of the paper -- that reconstruction
post-processing can lead to photon-noise limited sensitivity in the focal plane -- is weakened by
a lack of discussion of how such a reconstruction could be accomplished. While it may be
beyond the scope of this paper to present such a method in detail, the paper would be
strengthened by some discussion of the prospects of making the relevant measurements.

Response: We thank the referee for the careful review and insightful comments.  We have addressed each below.  In particular we have significantly expanded the discussion of post-processing to include an outline of a workable algorithm.

----------------------------------------------
Introduction

"Coronagraphic wavefront control"
Comment: This term should be defined.

Response: We agree that this is not well defined, and have changed to "post-coronagraph".

In paragraph 2 we changed the introduction of FPWFS and LOWFS to read:
".. various post-coronagraph focal-plane (e.g. Galicher et al. 2010) and low-order WFS&C strategies (e.g. Singh et al. 2017) show great promise in significantly reducing the impact of internal speckles."

And in paragraph 3 the last sentence now reads:
" The AO-corrected wavefront, though significantly improved, still causes a halo of speckles which will be
significantly brighter than the instrumental speckles in a high performance coronagraph
system employing the WFS&C strategies discussed above."

----------------------------------------------

Equation 2
Comment: Please give explicit definitions of all terms in the equation.

Response: The terms are now defined after the Equation:

"...where $\tau$ is the noise lifetime, $\sigma_o^2$ is the variance of a single measurement, $\sigma_{mean}^2$ is the variance in the estimate of the mean after time $t$"

----------------------------------------------

"Using AO-corrected images, Fitzgerald & Graham (2006) empirically found significantly longer
values of τ, giving an overall median of 175 ms at Lick observatory. Of note, the results of
Fitzgerald & Graham (2006) hinted that inside the region of the image plane controlled by the
AO system, the speckle lifetime was significantly shorter than outside."

Comment: It would be helpful to give the value of tau both inside and outside the control region
of the AO system here.

Response: We have removed this statement as it is over-interpreting the results of the cited paper.

----------------------------------------------

Section 2
"We could assume that delta_t is sufficiently short that the Is can be treated as a constant"
Comment: Perhaps I_s is a typo here, and should refer to I_*.

Response: This was meant to be a plural s and is confusing.  We have re-worded to:
"We could assume that delta_t is sufficiently short that the each of the I terms can be treated as constant"

and changed "Is" to "I terms" in the following sentence.

----------------------------------------------

Section 3
"This means that the mean is constant and the autocorrelation does not depend on time"
Comment: Given the variation of atmospheric turbulence, it would be helpful to justify this
assumption, and more broadly to justify the wide-sense stationary process.

Response: We have moved text from the Discussion to this point, adding "In this context, WSS essentially implies that the atmosphere parameters, namely $r_0$ and the layer $\vec{\mathcal{V}}$, are constant.  This is of course not strictly true, but can be expected to be approximately true over short periods of time, by which we mean at least long enough to estimate a PSD.  WSS also implies that AO control is stable, and we expect the control system to damp changes, keeping the output speckle formation process within a more or less well-defined range."

The relevant text in the discussion section now reads: "A key assumption underlying the mathematics of the PSD analysis is that the speckle intensity is wide-sense stationary (WSS), which means that the mean is constant and that the autocorrelation does not depend on time.  As discussed above, this assumption implies that $r_0$ and the layer $\vec{\mathcal{V}}$ are constant such that the statistics of the AO control output process are WSS.  In the simulations presented these assumptions are true by construction, and so the comparison to our semi-analytic predictions is valid.  On-sky input turbulence parameters will vary, and so the process will not be WSS over long periods.  However, these variations occur over finite times.  For our results to be useful the time-scales of these variations would need to be long enough to estimate a PSD which meaningfully captures the intensity dynamics.   What this ultimately means is that we must consider the speckle lifetime as itself a time-variable parameter, but we can expect there to be a representative value over an observation that characterizes long exposure sensitivity."

----------------------------------------------

Section 5
"The perfect 1st order coronagraph was simulated."
Comment: Please provide a citation here.

Response: We ave droped "1st order" and added a citation.  Te sentence now reads:
"The perfect coronagraph was simulated (Cavarroc et al. 2006)"

----------------------------------------------
Figure 7 caption "Note that the color bar is adjusted in each panel to best show detail."
Comment: Is the colorbar different for all eight panels, or is it the same for each pair of images
(e.g. is the colorbar for the calculated and simulated simple integrator panels the same)? If all
eight panels have different colorbars, they should be included in the figure.

Response: in both Figures 2 and 7 we have changed the text to read "The same colorbar is used for both calculated and simulated within a combination of controller and guidestar, but is adjusted to best show detail for each combination"
----------------------------------------------

Figure 8
Comment: Why do the calculations under-predict the speckle lifetimes at separations greater
than 10L/D for the infinitely bright, LP case?

Response: To address this, we have added additional text at the end of Section 5.4:
"The calculated and simulated lifetimes agree throughout most of the control region.  The noteworthy exception occurs in the LP roughly along a diagonal.  At wider separations the simulations predict lifetimes $\sim 50\%$ higher in a wedged shape region.  As with the differences in the phase dynamics discussed above, we attribute this to differences between the orthogonalized modal basis used in the simulations and the Fourier modes used in the calculations, and the resultant changes in the output of the controller coefficients and gain optimization."

And to the caption of Figure 8 we added: "The large difference in median lifetime between simulation and calculation for the LP is due to the wedge shaped region where the simulation predicts higher lifetimes (see Figure \ref{fig:lifetime_2Dcomp}.  See text for discussion."

----------------------------------------------
Section 6
"The LP controller shows much weaker dependence on the same parameters"

Comment: I find it particularly striking that the speckle lifetimes with the LP controller have a
much weaker dependence on the telescope diameter than the SI controller. Further discussion
of this point would be useful.

Response: We expanded discussion of this.  The text now reads: 
"The LP controller shows much weaker dependence on the same parameters.  Except at the lowest wind speeds, the speckle lifetime is $\sim$$20$ ms on the 5th-magnitude guide star with little variation.  Here the photon noise is well below the input turbulence PSD, and the LP can effectively whiten the disturbance to the photon noise floor.  The result is that the output PSD has the same shape, giving the same speckle lifetime regardless of the parameters.  On the 8th-magnitude star photon noise makes predictive control less effective, causing some variation with the parameters. There is a proportional scaling up to $D/\mathcal{V}$$\sim$$3$."

----------------------------------------------

"Interestingly, on the 8th-mag guide star and for the largest apertures the LP controller shows
the opposite trend. The power in each Fourier mode is proportional to 1/D2. Projected actuator
spacing was held constant, so the photon noise per mode is constant in these comparisons.
Furthermore, given the highest jet stream driven wind speeds we can expect, the GSMTs will
normally operate in the regime of D/V > 1. Thus the GSMTs are operating in a different regime
compared to the 6.5 m, and the LP controller produces different dynamics when photon noise
becomes important on the 8th-mag star."

Comment: The source of this different behavior with r0 is still unclear to me after reading this
discussion. The authors have mentioned several similarities and differences between the
different aperture cases, but the takeaway point regarding the r0 trends is not entirely clear.

Response:  We have added additional explanatory text.  The paragraph introducing the parameter analysis was re-worded to say:

"Note that the input power per Fourier mode scales as $D^{-2}$, that is it will be lower given larger $D$.  This means that the input temporal PSD has a different shape due to relative spatial frequency as well as different power due both to the wind speed and diameter. The input noise PSD will also be lower for each mode, but by $D^{-1}$ since the signal to noise ratio goes as S/N $\propto \sqrt{D}$.  The balance betwen these inputs can be expected to affect the performance of the optimized controllers, resulting in variation in speckle lifetimes."

The paragraph about r_0 now says:

"{For the SI controller, improving seeing (larger $r_0$) reduces speckle lifetime.  As the turbulence power is reduced, the control system is better able to reject low temporal frequencies, resulting in lower speckle lifetimes.  As with $D$ and $\mathcal{V}$, the LP controller shows little variation in lifetimes vs. $r_0$.  Here again, the predictive controller whitens the noise to the same floor set by photon noise, which produces an output PSD of roughly the same shape resulting in similar speckle lifetimes.  The lifetime increases somewhat vs $r_0$ on the larger diameters as the turbulence power becomes relatively lower compared to photon noise, resulting in reduced effectiveness of the predictor such that more correlations remain in the output."

----------------------------------------------

Section 7
Comment: This section is based on the supposition that "we have a technique for measuring the
Legendre mode coefficients an." It is difficult to evaluate the usefulness of this discussion
without understanding the prospects for making such measurements. Perhaps the authors could
weigh in on how or whether the mode coefficients could be measured with current or future
instruments.

Response: We have added a brief introduction to AO PSF reconstruction, and provided an outline of the basic algorithm needed to perform reconstruction
for high-contrast imaging.  The new text read:

[TODO: add text once we're all happy with it]

----------------------------------------------
Section 8
"A key assumption underlying the mathematics of the PSD analysis is that the speckle intensity
is WSS"
Comment: I suggest moving this discussion to the earlier section when the WSS argument was
initially made, or summarizing it there, to help the audience understand the validity of the WSS
argument when it is first introduced.

Response: Addressed in comment above -- we added more discussion in section 3, and re-worded this paragraph to read:

"A key assumption underlying the mathematics of the PSD analysis is that the speckle intensity is wide-sense stationary (WSS), which means that the mean is constant and that the autocorrelation does not depend on time.  As discussed above, this assumption implies that $r_0$ and the layer $\vec{\mathcal{V}}$ are constant such that the statistics of the AO control output process are WSS.  In the simulations presented these assumptions are true by construction, and so the comparison to our semi-analytic predictions is valid.  On-sky input turbulence parameters will vary, and so the process will not be WSS over long periods.  However, these variations occur over finite times.  For our results to be useful the time-scales of these variations would need to be long enough to estimate a PSD which meaningfully captures the intensity dynamics.   What this ultimately means is that we must consider the speckle lifetime as itself a time-variable parameter, but we can expect there to be a representative value over an observation that characterizes long exposure sensitivity."

----------------------------------------------

Section 9
"We have shown that the speckle lifetime is an order of magnitude shorter than previous studies
have found"
Comment: Unless I'm mistaken, this point was not explicitly made in the body of the paper.

Response: This point was not made explicity.  We added the following paragraph at the end of Section 5.4:

"For comparison, the ``crossing-time'' speckle lifetime of \citet{2005SPIE.5903..170M} would be $\tau=0.3D/\mathcal{V} = 224$ ms for the turbulence averaged windspeed used in these calculations, with the caveat that the constant of propotionality is expected to vary with coronagraph. We find lifetimes much shorter than this, up to a factor of 10 shorter for the LP controller. Figures \ref{fig:lifetime_2Dcomp} and \ref{fig:lifetime_radprof} show that speckle lifetime has a strong dependence on control law, and varies with position in the image.  We investigate the $D/\mathcal{V}$ scaling next."
----------------------------------------------

### 2021-05-24 specklelives.tex
updated

For some time, long-lived ``quasi-static'' speckles have been recognized as the limiting noise source in contemporary high contrast imaging observations \citep[e.g.][]{2007ApJ...654..633H}.  Given their origin within the instrument, and comparatively long lifetimes \citep{2012A&A...541A.136M}, such speckles should be suppressible using wavefront sensing and control (WFS\&C) strategies.  Recent progress in applying ``dark hole'' contrast optimization with focal plane WFS \citep{2020A&A...638A.117P} and various focal-plane \citep[e.g.][]{2010A&A...509A..31G} and low-order coronagraphic WFS\&C strategies \citep[e.g.][]{2017PASP..129i5002S} show great promise in significantly reducing the impact of internal speckles.  Once active quasi-static speckle control becomes routine, the fundamental sensitivity limit in ground-based high-contrast imaging will be set by the Earth's atmosphere.

@@

Speckles also arise from atmospheric turbulence.  The index of refraction of air depends on temperature, and turbulence causes the air temperature to stochastically vary across the telescope aperture.  As the stellar wavefront traverses these regions of different index of refraction, parts of the wavefront travel different optical path lengths.  Due mainly to wind-driven bulk flow across the telescope aperture, the atmospheric temperature structure is constantly changing.  The technique of adaptive optics (AO) is used to correct the resulting time-variable optical aberrations in real time.  Even with so-called ``extreme'' AO systems \citep[ExAO, ][]{2018ARAA..56..315G} this correction is imperfect.  The AO-corrected wavefront, though significantly improved, still causes a halo of speckles significantly brighter than the instrumental speckles in a modern high performance coronagraph system using coronagraphic wavefront control.

@@

\subsection{Variance of the Mean}
The autocorrelation e-folding time is a somewhat arbitrary choice.  If we instead consider the evolution of the variance in the estimate of the mean given uncorrelated trials, we can define the speckle lifetime according to the familiar ``root-N'' reduction in noise:
\begin{equation}
\sigma_{mean}^2 = \frac{\sigma_o^2}{t/\tau}
\label{eqn:varmean_def_intro}
\end{equation}
This simply states that the variance in a measurement of the mean improves with the number of uncorrelated trials $t/\tau$.  Defined this way, $\tau$ is given by the integral of the autocorrelation \citep{2006ApJ...637..541F}, and in this expression determines the number of uncorrelated realizations of the speckle pattern included in the mean.  Note that this assumes $t \gg \tau$.  \citet{1986JOSAA...3.1001A} employed this definition, and argued for longer speckle lifetimes, replacing $0.36$ by $~$$1.14$ in Equation (\ref{eqn:e-fold}) based on arguments similar to \citet{1982JOpt...13..263R}.  Using AO-corrected images, \citet{2006ApJ...637..541F} empirically found significantly longer values of $\tau$, giving an overall median of 175 ms at Lick observatory.  Of note, the results of \citet{2006ApJ...637..541F} hinted that inside the region of the image plane controlled by the AO system, the speckle lifetime was significantly shorter than outside.

@@

We have likewise dropped the $t$ dependence, but we note that this is somewhat subtle.  We could assume that $\Delta t$ is sufficiently short that the $I$s can be treated as constant, and then state the long exposure variance as a sum of the variance in these short exposures.  Alternatively, we can treat the $I$s in Equation (\ref{eqn:variance}) as mean values, and then $\sigma^2_{h}$ is the mean of the variance.  For large total exposure time these will converge.

@@

We assume that $I(t)$ is a wide-sense stationary (WSS) process.  This means that the mean is constant and the autocorrelation does not depend on time.  With the WSS assumption, the Wiener-Khinchin theorem states that the PSD is the Fourier transform of the autocorrelation.  The PSD then describes how the measurements derived from the process are correlated. \citet{1976JOSA...66..207N} exploited this concept in two dimensions to derive the coefficient covariances in the Zernike polynomial expansion of Kolmogorov turbulence phase screens.  Here we adapt that analysis to arbitrary one dimensional PSDs using the Legendre polynomials.

@@

\begin{figure}
\hspace{-0.3in}
\includegraphics[width=3.54in]{contrast0mag.pdf}
\includegraphics[width=3.54in]{contrast8mag.pdf}
\caption{Comparison of long-exposure raw contrast from semi-analytic calculations (Section \ref{sec:recipe}) and end-to-end simulation (Section \ref{sec:simulations}) for a 6.5 m telescope. Left: without photon noise, considering the input turbulence only.  Right: with photon noise on an 8th mag star assuming the sensitivity of an unmodulated pyramid WFS. Note that the color bar is adjusted to best show detail.  The agreement between the calculations and simulations shows that the model is accurate.\label{fig:contrast_2Dcomp}}
\end{figure}

@@

Finally in Figure \ref{fig:lifetime_2Dcomp} we present maps of speckle lifetime, and in Figure \ref{fig:lifetime_radprof} the median radial profile of speckle lifetime.  Overall these results show that Equation (\ref{eqn:psd_lifetime}) correctly describes the statistical speckle lifetime for a given intensity PSD, which in turn can be predicted by our semi-analytic model of an ExAO coronagraph.

\begin{figure}
\hspace{-0.3in}
\includegraphics[width=3.54in]{lifetimes0mag.pdf}
\includegraphics[width=3.54in]{lifetimes8mag.pdf}
\caption{Comparison of model predictions for speckle lifetime to end-to-end simulation for a 6.5 m telescope.  Left: without photon noise, considering the input turbulence only.  Right: with photon noise on an 8th mag star assuming the sensitivity of an unmodulated pyramid WFS. Note that the color bar is adjusted in each panel to best show detail. For the integrator the agreement is very good.  For the predictor on the infinitely bright star, the agreement is good overall but the calculations modestly over-predict speckle lifetimes in a wedge associated with (but not parallel to) the wind vectors.  This results demonstrate that AO control does affect speckle lifetimes, and that the lifetime is significantly shorter under predictive control.  The lifetime also depends on location in the control region. \label{fig:lifetime_2Dcomp}}
\end{figure}

\begin{figure}
\hspace{-0.3in}
\includegraphics[width=6.5in]{lifetimesRP.pdf}
\caption{Median radial profiles of the lifetime maps shown in Figure \ref{fig:lifetime_2Dcomp}.  Left: without photon noise, considering the input turbulence only.  Right: with photon noise on an 8th mag star assuming the sensitivity of an unmodulated pyramid WFS. Speckle lifetime is shorter under predictive control compared to the simple integrator. \label{fig:lifetime_radprof}}
\end{figure}

%\clearpage

@@

Next, we analyze the change in speckle lifetime with guide star brightness, telescope diameter, wind speed, and seeing.  Note that power per Fourier mode scales as $D^{-2}$.  We held relative spatial frequency constant with $D$, such that the resultant speckle occurs at the same relative projected separation in $\lambda/D$ units.   This means that the input temporal PSD has a different shape as well as different power.  This compares the performance of coronagraphic AO systems given the improvement in spatial resolution with $D$.

@@

The SI controller, in general, shows a decrease in lifetime with wind speed $\mathcal{V}$ and an increase with diameter $D$ for both guide stars.  When analyzed as the crossing time $D/\mathcal{V}$, the SI controller scales roughly proportional to the crossing-time up to $D/\mathcal{V}$$\sim$$2$.  For longer crossing times the trend becomes flat.  This implies that the control system becomes dominated by photon noise rather than servo lag and so the optimization process no longer produces changes in the output dynamics.

The LP controller shows much weaker dependence on the same parameters.  Except at the lowest wind speeds, the speckle lifetime is $\sim$$20$ ms on the 5th-magnitude guide star.  On the 8th-magnitude star photon noise makes predictive control less effective, and there is a proportional scaling up to $D/\mathcal{V}$$\sim$$3$.

In most cases, improving seeing (larger $r_0$), reduces speckle lifetime.  As the turbulence power is reduced, the control system is better able to reject low temporal frequencies, resulting in lower speckle lifetimes.  Interestingly, on the 8th-mag guide star and for the largest apertures the LP controller shows the opposite trend.  The power in each Fourier mode is proportional to $1/D^2$.  Projected actuator spacing was held constant, so the photon noise per mode is constant in these comparisons.  Furthermore, given the highest jet stream driven wind speeds we can expect, the GSMTs will normally operate in the regime of $D/\mathcal{V} \gtrsim 1$.  Thus the GSMTs are operating in a different regime compared to the 6.5 m, and the LP controller produces different dynamics  when photon noise becomes important on the 8th-mag star.

\section{The Potential of Reconstruction Post-Processing}
\label{sec:reconstruction}
\textbf{A closed-loop wavefront control system measures the coefficients of the controlled modes in the residual wavefront at each loop time step.  In this analysis we have treated the Fourier basis, with modal coefficients $h_{mn}^{p}(t)$.   The residual phase is reconstructed as in Equation \ref{eqn:phi_expansion}.  The control system could use any modal basis, and the phase reconstructed in equivalent fashion. More realistic coronagraphs can be modeled, and the wavefront propagated through the system model.  }.

\textbf{Here we continue analyzing an ExAO system controlling in the Fourier basis, which will produce measured coefficients $\Delta h_{mn}^{p}(t)$ which we assume are recorded for later analysis.  Additionally we assume, for now, that focal plane intensity is recorded with a detector reading out at the same rate as and synchronized to the WFS, such that measurements $I_{mn}(t)$ are recorded at each pixel. The measured focal plane intensity may include signal from a planet in addition to scattered starlight. Our goal is to use the measured modal coefficients to estimate the contribution from scattered starlight, so that any planet signal can be measured.}

\textbf{To accomplish this goal, at some later time we use the measured residual coefficients to reconstruct an estimate of the focal plane intensity due to scattered starlight alone.  To begin, we reconstruct the residual phase based on Equation \ref{eqn:phi_expansion} }
\begin{equation}
\Delta\Phi(\vec{q},t) = \frac{2\pi}{\lambda} \sum\limits_{mn} \left[ \Delta h_{mn}^{+}(t) M_{mn}^{+}(\vec{q}) + \Delta h_{mn}^{-}(t) M_{mn}^{-}(\vec{q})\right]
\label{eqn:phi_residual}
\end{equation}
\textbf{We then propagate the residual phase to the focal plane}
\begin{equation}
\hat{I}(\vec{r},t) = G \left\{\mathcal{A}(\vec{q}) \mbox{e}^{i\Delta\Phi(\vec{q},t)} \right\}
\end{equation}
\textbf{where $G\{\cdot\}$ is the system propagation operator, which includes the effect of the coronagraph.  See \citet{2017MNRAS.467L.105H} for an example of the construction of such a model. In the case of the perfect coronagraph used in this work, the propagation operator reduces to  Equation \ref{eqn:cross_terms}. The result is an estimated intensity time series at position $\vec{r}_{mn}$ }
\begin{equation}
\hat{I}_{mn}(t) = \hat{I}(\vec{r}_{mn},t)
\end{equation}

>>>>

For some time, long-lived ``quasi-static'' speckles have been recognized as the limiting noise source in contemporary high contrast imaging observations \citep[e.g.][]{2007ApJ...654..633H}.  Given their origin within the instrument, and comparatively long lifetimes \citep{2012A&A...541A.136M}, such speckles should be suppressible using wavefront sensing and control (WFS\&C) strategies.  Recent progress in applying ``dark hole'' contrast optimization with focal plane WFS \citep{2020A&A...638A.117P} and various \textbf{post-coronagraph} focal-plane \citep[e.g.][]{2010A&A...509A..31G} and low-order  WFS\&C strategies \citep[e.g.][]{2017PASP..129i5002S} show great promise in significantly reducing the impact of internal speckles.  Once active quasi-static speckle control becomes routine, the fundamental sensitivity limit in ground-based high-contrast imaging will be set by the Earth's atmosphere.

@@

Speckles also arise from atmospheric turbulence.  The index of refraction of air depends on temperature, and turbulence causes the air temperature to stochastically vary across the telescope aperture.  As the stellar wavefront traverses these regions of different index of refraction, parts of the wavefront travel different optical path lengths.  Due mainly to wind-driven bulk flow across the telescope aperture, the atmospheric temperature structure is constantly changing.  The technique of adaptive optics (AO) is used to correct the resulting time-variable optical aberrations in real time.  Even with so-called ``extreme'' AO systems \citep[ExAO, ][]{2018ARAA..56..315G} this correction is imperfect.  The AO-corrected wavefront, though significantly improved, still causes a halo of speckles \textbf{which will be significantly brighter than the instrumental speckles in a high performance coronagraph system employing the WFS\&C strategies discussed above}.

@@

\subsection{Variance of the Mean}
The autocorrelation e-folding time is a somewhat arbitrary choice.  If we instead consider the evolution of the variance in the estimate of the mean given uncorrelated trials, we can define the speckle lifetime according to the familiar ``root-N'' reduction in noise:
\begin{equation}
\sigma_{mean}^2 = \frac{\sigma_o^2}{t/\tau}
\label{eqn:varmean_def_intro}
\end{equation}
\textbf{where $\tau$ is the noise lifetime, $\sigma_o^2$ is the variance of a single measurement, $\sigma_{mean}^2$ is the variance in the estimate of the mean after time $t$}.  This simply states that the variance in a measurement of the mean improves with the number of uncorrelated trials $t/\tau$.  Defined this way, $\tau$ is given by the integral of the autocorrelation \citep{2006ApJ...637..541F}, and in this expression determines the number of uncorrelated realizations of the speckle pattern included in the mean.  Note that this assumes $t \gg \tau$.  \citet{1986JOSAA...3.1001A} employed this definition, and argued for longer speckle lifetimes, replacing $0.36$ by $~$$1.14$ in Equation (\ref{eqn:e-fold}) based on arguments similar to \citet{1982JOpt...13..263R}.  Using AO-corrected images, \citet{2006ApJ...637..541F} empirically found significantly longer values of $\tau$, giving an overall median of 175 ms at Lick observatory.  
%Of note, the results of \citet{2006ApJ...637..541F} hinted that inside the region of the image plane controlled by the AO system, the speckle lifetime was significantly shorter than outside.

@@

We have likewise dropped the $t$ dependence, but we note that this is somewhat subtle.  We could assume that $\Delta t$ is sufficiently short that the \textbf{each of the $\mathcal{I}$ terms} can be treated as constant, and then state the long exposure variance as a sum of the variance in these short exposures.  Alternatively, we can treat the $\mathcal{I}$ terms in Equation (\ref{eqn:variance}) as mean values, and then $\sigma^2_{h}$ is the mean of the variance.  For large total exposure time these will converge.

@@

We assume that $I(t)$ is a wide-sense stationary (WSS) process.  This means that the mean is constant and the autocorrelation does not depend on time.   \textbf{In this context, WSS essentially implies that the atmosphere parameters, namely $r_0$ and the layer $\vec{\mathcal{V}}$, are constant.  This is of course not strictly true, but can be expected to be approximately true over short periods of time, by which we mean at least long enough to estimate a PSD.  WSS also implies that AO control is stable, and we expect the control system to damp changes, keeping the output speckle formation process within a more or less well-defined range.}

With the WSS assumption, the Wiener-Khinchin theorem states that the PSD is the Fourier transform of the autocorrelation. The PSD then describes how the measurements derived from the process are correlated. \citet{1976JOSA...66..207N} exploited this concept in two dimensions to derive the coefficient covariances in the Zernike polynomial expansion of Kolmogorov turbulence phase screens.  Here we adapt that analysis to arbitrary one dimensional PSDs using the Legendre polynomials.

@@

\begin{figure}
\hspace{-0.3in}
\includegraphics[width=3.54in]{contrast0mag.pdf}
\includegraphics[width=3.54in]{contrast8mag.pdf}
\caption{Comparison of long-exposure raw contrast from semi-analytic calculations (Section \ref{sec:recipe}) and end-to-end simulation (Section \ref{sec:simulations}) for a 6.5 m telescope. Left: without photon noise, considering the input turbulence only.  Right: with photon noise on an 8th mag star assuming the sensitivity of an unmodulated pyramid WFS. \textbf{The same colorbar is used for both calculated and simulated within a combination of controller and guidestar, but is adjusted to best show detail for each combination}.  The agreement between the calculations and simulations shows that the model is accurate.\label{fig:contrast_2Dcomp}}
\end{figure}

@@

Finally in Figure \ref{fig:lifetime_2Dcomp} we present maps of speckle lifetime, and in Figure \ref{fig:lifetime_radprof} the median radial profile of speckle lifetime. \textbf{The calculated and simulated lifetimes agree throughout most of the control region.  The noteworthy exception occurs in the LP roughly along a diagonal.  At wider separations the simulations predict lifetimes $\sim 50\%$ higher in a wedged shape region.  As with the differences in the phase dynamics discussed above, we attribute this to differences between the orthogonalized modal basis used in the simulations and the Fourier modes used in the calcualtions, and the resultant changes in the output of the controller coefficients and gain optimization.}

\textbf{For comparison, the ``crossing-time'' speckle lifetime of \citet{2005SPIE.5903..170M} would be $\tau=0.3D/\mathcal{V} = 224$ ms for the turbulence averaged windspeed used in these calculations, with the caveat that the constant of propotionality is expected to vary with coronagraph. We find lifetimes much shorter than this, up to a factor of 10 shorter for the LP controller. Figures \ref{fig:lifetime_2Dcomp} and \ref{fig:lifetime_radprof} show that speckle lifetime has a strong dependence on control law, and varies with position in the image.  We investigate the $D/\mathcal{V}$ scaling below.}

Overall these results show that Equation (\ref{eqn:psd_lifetime}) correctly describes the statistical speckle lifetime for a given intensity PSD, which in turn can be predicted by our semi-analytic model of an ExAO coronagraph.

\begin{figure}
\hspace{-0.3in}
\includegraphics[width=3.54in]{lifetimes0mag.pdf}
\includegraphics[width=3.54in]{lifetimes8mag.pdf}
\caption{Comparison of model predictions for speckle lifetime to end-to-end simulation for a 6.5 m telescope.  Left: without photon noise, considering the input turbulence only.  Right: with photon noise on an 8th mag star assuming the sensitivity of an unmodulated pyramid WFS. \textbf{The same colorbar is used for both calculated and simulated within a combination of controller and guidestar, but is adjusted to best show detail for each combination}. For the integrator the agreement is very good.  For the predictor on the infinitely bright star, the agreement is good overall but the calculations modestly over-predict speckle lifetimes in a wedge associated with (but not parallel to) the wind vectors.  These results demonstrate that AO control does affect speckle lifetimes, and that the lifetime is significantly shorter under predictive control.  The lifetime also depends on location in the control region. \label{fig:lifetime_2Dcomp}}
\end{figure}

\begin{figure}
\hspace{-0.3in}
\includegraphics[width=6.5in]{lifetimesRP.pdf}
\caption{Median radial profiles of the lifetime maps shown in Figure \ref{fig:lifetime_2Dcomp}.  Left: without photon noise, considering the input turbulence only.  Right: with photon noise on an 8th mag star assuming the sensitivity of an unmodulated pyramid WFS. Speckle lifetime is shorter under predictive control compared to the simple integrator. \textbf{The large difference in median lifetime between simulation and calculation for the LP is due to the wedge shaped region where the simulation predicts higher lifetimes (see Figure \ref{fig:lifetime_2Dcomp}.  See text for discussion.}  \label{fig:lifetime_radprof}}
\end{figure}

\clearpage

@@

Next, we analyze the change in speckle lifetime with guide star brightness, telescope diameter, wind speed, and seeing.   We held relative spatial frequency constant with $D$, such that the resultant speckle occurs at the same relative projected separation in $\lambda/D$ units.  This compares the performance of coronagraphic AO systems given the improvement in spatial resolution with $D$.  \textbf{Note that the input power per Fourier mode scales as $D^{-2}$, that is it will be lower given larger $D$.  This means that the input temporal PSD has a different shape due to relative spatial frequency as well as different power due to both the wind speed and diameter. The input noise PSD will also be lower for each mode, but by $D^{-1}$ since the signal to noise ratio goes as S/N $\propto \sqrt{D}$.  The balance betwen these inputs can be expected to affect the performance of the optimized controllers, resulting in variation in speckle lifetimes.}

@@

The SI controller, in general, shows a decrease in lifetime with wind speed $\mathcal{V}$ and an increase with diameter $D$ for both guide stars.  When analyzed as the crossing time $D/\mathcal{V}$, the SI controller scales roughly proportional to the crossing-time up to $D/\mathcal{V}$ $\sim$ $2$.  For longer crossing times the trend becomes flat.  This implies that the control system becomes dominated by photon noise rather than servo lag and so the optimization process no longer produces changes in the output dynamics.

\textbf{The LP controller shows much weaker dependence on the same parameters.  Except at the lowest wind speeds, the speckle lifetime is $\sim$$20$ ms on the 5th-magnitude guide star with little variation.  Here the photon noise is well below the input turbulence PSD, and the LP can effectively whiten the disturbance to the photon noise floor.  The result is that the output PSD has the same shape, giving the same speckle lifetime regardless of the parameters.  On the 8th-magnitude star photon noise makes predictive control less effective, causing some variation with the parameters. There is a proportional scaling up to $D/\mathcal{V}$$\sim$$3$.}

\textbf{For the SI controller, improving seeing (larger $r_0$) reduces speckle lifetime.  As the turbulence power is reduced, the control system is better able to reject low temporal frequencies, resulting in lower speckle lifetimes.  As with $D$ and $\mathcal{V}$, the LP controller shows little variation in lifetimes vs. $r_0$.  Here again, the predictive controller whitens the noise to the same floor set by photon noise, which produces an output PSD of roughly the same shape resulting in similar speckle lifetimes.  The lifetime increases somewhat vs $r_0$ on the larger diameters as the turbulence power becomes relatively lower compared to photon noise, resulting in reduced effectiveness of the predictor such that more correlations remain in the output. }

\section{The Potential of \textbf{PSF} Reconstruction Post-Processing}
\label{sec:reconstruction}
\textbf{The reconstruction of the post-AO PSF using AO system telemetry has been studied for some time, primarily focused on the long-exposure PSF, e.g. \citet{1997JOSAA..14.3057V} and see the recent review by \citep{2020SPIE11448E..0AB}.  PSF reconstruction in the context of high-contrast imaging is mainly concerned with short exposures and typically has been based on image data alone \citep{2006ApJ...641..556M,2007ApJ...660..770L,2012ApJ...755L..28S}, however the potential for telemetry-based PSF estimation in high-contrast imaging has been recognized \citep{2013ApJ...767...21F,2013ApJ...767..100C}. Here we use our treatment of the intensity dynamics behind an AO-fed coronagraph to analyze the performance of PSF estimation and subtraction, particularly motivated by the use of WFS telemetry to improve on the sensitivity limit set by atmospheric speckle lifetimes.}

\textbf{A closed-loop wavefront control system measures the coefficients of the controlled modes in the residual wavefront at each loop time step.  The WFS produces measurements of the residual phase with modal coefficients $\Delta h_{mn}^{p}(t)$ which we assume are recorded. Additionally we assume that focal plane intensity is recorded with a detector reading out at the same rate as and synchronized to the WFS, such that measurements $I_{mn}(t)$ are recorded at each pixel. The measured focal plane intensity may include signal from a planet in addition to scattered starlight.}

\textbf{At some later time we use the measured residual coefficients to reconstruct an estimate of the focal plane intensity due to scattered starlight alone.  To begin, we reconstruct the residual phase based on Equation \ref{eqn:phi_expansion} }
\begin{equation}
\Delta\Phi(\vec{q},t) = \frac{2\pi}{\lambda} \sum\limits_{mn} \left[ \Delta h_{mn}^{+}(t) M_{mn}^{+}(\vec{q}) + \Delta h_{mn}^{-}(t) M_{mn}^{-}(\vec{q})\right].
\label{eqn:phi_residual}
\end{equation}
\textbf{We then propagate the residual phase to the focal plane}
\begin{equation}
\hat{I}(\vec{r},t) = G \left\{\mathcal{A}(\vec{q}) \mbox{e}^{i\Delta\Phi(\vec{q},t)} \right\}
\end{equation}
\textbf{where $\mathcal{A}(\vec{q})$ defines the pupil and $G\{\cdot\}$ is the system propagation operator, which could include information such as the effect of the coronagraph, non-common path aberrations (not sensed by the WFS which measures the $\Delta h_{mn}^{p}(t)$), and Fresnel propagation.  See \citet{2017MNRAS.467L.105H} for an example of the construction of such a model. In the case of the perfect coronagraph and ideal optical system used in this work, the propagation operator reduces to Equation \ref{eqn:cross_terms}. The result of applying $G\{\cdot\}$ to the reconstructed wavefront is an estimated intensity time series at position $\vec{r}_{mn}$ }
\begin{equation}
\hat{I}_{mn}(t) = \hat{I}(\vec{r}_{mn},t)
\end{equation}
